---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggsaves

<!-- badges: start -->
[![R-CMD-check](https://github.com/selkamand/ggsaves/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/ggsaves/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/ggsaves)](https://CRAN.R-project.org/package=ggsaves)
<!-- badges: end -->

ggsaves saves a ggplot as a PDF, 300dpi PNG, and SVG all at once. This is an exceptionally simple convenience package that wraps `ggplot2::ggsave()`.

It can also save ggiraph objects in html, svg, and png formats with `ggisaves`

## Installation

Install ggsaves from CRAN

```{r}
install.packages('ggsaves')
```


Alternatively, install the development version of ggsaves from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/ggsaves")
```

## Quick Start

Saving a ggplot

```{r example, eval=FALSE}
library(ggplot2)
library(ggsaves)

gg_plot <- mtcars |> 
  ggplot(aes(mpg, cyl)) + 
  geom_point() 

ggsaves(gg_plot, prefix = "myplot",  outfolder = ".")
```

Saving a ggiraph plot

```{r, eval=FALSE}
library(ggiraph)
gg_plot <- iris |> 
  ggplot(aes(Sepal.Length, Sepal.Width)) + 
  geom_point_interactive(aes(data_id  = Species, tooltip = Species))

 interactive_gg_plot <- girafe(ggobj = gg_plot)
 
 ggisaves(interactive_gg_plot, prefix = "my_interactive_plot", outfolder = ".")
```


